---
title: "QC Report"
date: "Report generated: `r format(Sys.time())`"
output:
      html_document:
      highlight: tango
      code_folding: hide
        # number_sections: yes
        # toc: yes
        # toc_depth: 2
        # toc_float: yes
params:
  experiment: NA
  bcl.dir: NA
  amp.match.summary: NA
  seq.metrics: NA
  samples_with_ids: NA
  samples_to_report: NA
  dlong: NA
  dwide: NA
---

# `r paste("Experiment:", params$experiment)`

```{r include=FALSE}
#library(ggplot2)
#library(knitr)
#library(DT)
#library(XML)

xmlinfo=XML::xmlToList(XML::xmlParse(paste0(params$bcl.dir, 'RunParameters.xml')))
chemistry=xmlinfo$Chemistry
#MiniSeq High / MiniSeq Rapid High / NextSeq Mid / NextSeq High
instrument=xmlinfo$ComputerName
FlowCellInfo=xmlinfo$FlowCellRfidTag
ReagentKitInfo=xmlinfo$ReagentKitRfidTag
# library(ggpubr)
```
#### `r paste("BCL Directory:",  xmlinfo$RunID)`
#### `r paste("Instrument:",  instrument,  xmlinfo$InstrumentID)`
#### `r paste("Chemistry:",  chemistry)`
#### `r paste("Start Time:", xmlinfo$RunStartTimeStamp)`
******


## Sequencer metrics
```{r echo=FALSE}
params$seq.metrics %>%
knitr::kable()
```

## FlowCell Info
```{r echo=FALSE}
data.frame(FlowCellInfo) %>%
knitr::kable()
```

## ReagentKit Info
```{r echo=FALSE}
data.frame(ReagentKitInfo) %>%
knitr::kable()
```

## Alignment summary
```{r echo=FALSE}
params$amp.match.summary %>% 
knitr::kable()
```

## Results Summary
```{r echo=FALSE}
results.summary=data.frame(
    'TotalSamplesPocessed'=sum(params$samples_to_report),                         
    'Inconclusives'=sum(params$dwide$result[params$samples_to_report]=='Inconclusive'),
    'NoVirusDetected'=sum(params$dwide$result[params$samples_to_report]=='Negative'),
    'VirusDetected'=sum(params$dwide$result[params$samples_to_report]=='Positive'))
results.summary %>% 
    knitr::kable()
```

# Plate Maps {.tabset .tabset-fade}

## Plate maps (384)
```{r echo=FALSE, fig.height=10, fig.width=12}
IndexSet=params$dlong$Plate_ID
IndexSet[params$dlong$IndexSet %in% c('Plate1', 'Plate2', 'Plate3', 'Plate4')]='Winter'
IndexSet[params$dlong$IndexSet %in% c('Plate5', 'Plate6', 'Plate7', 'Plate8')]='Spring'
IndexSet[params$dlong$IndexSet %in% c('Plate9', 'Plate10', 'Plate11', 'Plate12') ]='Summer'
IndexSet[params$dlong$IndexSet %in% c('Plate13', 'Plate14', 'Plate15', 'Plate16')]='Fall'

IndexSetW=params$dwide$Plate_ID
IndexSetW[params$dwide$IndexSet %in% c('Plate1', 'Plate2', 'Plate3', 'Plate4')]='Winter'
IndexSetW[params$dwide$IndexSet %in% c('Plate5', 'Plate6', 'Plate7', 'Plate8')]='Spring'
IndexSetW[params$dwide$IndexSet %in% c('Plate9', 'Plate10', 'Plate11', 'Plate12') ]='Summer'
IndexSetW[params$dwide$IndexSet %in% c('Plate13', 'Plate14', 'Plate15', 'Plate16')]='Fall'

psplit=split(params$dlong, IndexSet)
lapply(psplit, function(x) {
           x%>%
#params$dlong %>%  
ggplot2::ggplot(ggplot2::aes(x=Col, y=Row, fill=log10(Count))) + 
  ggplot2::geom_raster() +
  ggplot2::coord_equal() +
  ggplot2::facet_grid(amplicon~Plate_384+Plate_ID) +
  ggplot2::scale_fill_viridis_c(option = 'plasma')+ggplot2::ggtitle(params$experiment)
    })
```

## Tube locations (384)
```{r echo=FALSE, fig.height=10, fig.width=12}
psplit=split(params$dwide, IndexSetW)
lapply(psplit, function(x) {
           x%>%
#params$dwide %>% 
ggplot2::ggplot(ggplot2::aes(x=Col, y=Row, fill=matrix_tube_present)) + 
  ggplot2::geom_raster() +
  ggplot2::coord_equal() +
  ggplot2::facet_grid(~Plate_384+Plate_ID) +
  #scale_fill_viridis_c(option = 'plasma')+
  ggplot2::ggtitle(params$experiment)
    })
```


## Swabseq Calls (384)
```{r echo=FALSE, fig.height=10, fig.width=12}
psplit=split(params$dwide, IndexSetW)
lapply(psplit, function(x) {
           x%>%
#params$dwide %>% 
ggplot2::ggplot(ggplot2::aes(x=Col, y=Row, fill=result)) + 
  ggplot2::geom_raster() +
  ggplot2::coord_equal() +
  ggplot2::facet_grid(~Plate_384+Plate_ID) +
  #scale_fill_viridis_c(option = 'plasma')+
  ggplot2::ggtitle(params$experiment)
    })
```

## S2 and S2 spike QC (384)
```{r echo=FALSE, fig.height=10, fig.width=12}
psplit=split(params$dwide,IndexSetW)
lapply(psplit, function(x) {
           x%>%
#params$dwide %>% 
ggplot2::ggplot(ggplot2::aes(x=Col, y=Row, fill=Stotal>cfg$coreVars$Stotal)) + 
  ggplot2::geom_raster() +
  ggplot2::coord_equal() +
  ggplot2::facet_grid(~Plate_384+Plate_ID) +
  #scale_fill_viridis_c(option = 'plasma')+
  ggplot2::ggtitle(params$experiment) })
```

## RPP30 QC (384)
```{r echo=FALSE, fig.height=10, fig.width=12}
psplit=split(params$dwide, IndexSetW)
lapply(psplit, function(x) {
           x%>%
#params$dwide %>% 
ggplot2::ggplot(ggplot2::aes(x=Col, y=Row, fill=RPP30_Detected)) + 
  ggplot2::geom_raster() +
  ggplot2::coord_equal() +
  ggplot2::facet_grid(~Plate_384+Plate_ID) +
  #scale_fill_viridis_c(option = 'plasma')+
  ggplot2::ggtitle(params$experiment)
  })
```

## Plate maps (96)
```{r echo=FALSE, fig.height=10, fig.width=12}
psplit=split(params$dlong, params$dlong$Plate_384)
lapply(psplit, function(x) {
           x%>%
  ggplot2::ggplot(ggplot2::aes(x=Col96, y=Row96, fill=log10(Count))) + 
  ggplot2::geom_raster() +
  ggplot2::coord_equal() +
  ggplot2::facet_grid(amplicon~Plate_384+Plate_ID+quadrant_96) +
  ggplot2::scale_fill_viridis_c(option = 'plasma')+ggplot2::ggtitle(params$experiment)
})
```

## Tube locations (96)
```{r echo=FALSE, fig.height=10, fig.width=12}
psplit=split(params$dwide, params$dwide$Plate_384)
lapply(psplit, function(x) {
           x%>%
ggplot2::ggplot(ggplot2::aes(x=Col96, y=Row96, fill=matrix_tube_present)) + 
  ggplot2::geom_raster() +
  ggplot2::coord_equal() +
  ggplot2::facet_grid(~Plate_384+Plate_ID+quadrant_96) +
  #scale_fill_viridis_c(option = 'plasma')+
  ggplot2::ggtitle(params$experiment)
})
```

## S2 and S2 spike QC (96)
```{r echo=FALSE, fig.height=10, fig.width=12}
psplit=split(params$dwide, params$dwide$Plate_384)
lapply(psplit, function(x) {
           x%>%
ggplot2::ggplot(ggplot2::aes(x=Col96, y=Row96, fill=Stotal>500)) + 
  ggplot2::geom_raster() +
  ggplot2::coord_equal() +
  ggplot2::facet_grid(~Plate_384+Plate_ID+quadrant_96) +
  #scale_fill_viridis_c(option = 'plasma')+
  ggplot2::ggtitle(params$experiment)
})
```

## RPP30 QC (96)
```{r echo=FALSE, fig.height=10, fig.width=12}
psplit=split(params$dwide, params$dwide$Plate_384)
lapply(psplit, function(x) {
           x%>%
ggplot2::ggplot(ggplot2::aes(x=Col96, y=Row96, fill=RPP30_Detected)) + 
  ggplot2::geom_raster() +
  ggplot2::coord_equal() +
  ggplot2::facet_grid(~Plate_384+Plate_ID+quadrant_96) +
  #scale_fill_viridis_c(option = 'plasma')+
  ggplot2::ggtitle(params$experiment)
})
```

## Swabseq Calls (96)
```{r echo=FALSE, fig.height=10, fig.width=12}
psplit=split(params$dwide, params$dwide$Plate_384)
lapply(psplit, function(x) {
           x%>%
ggplot2::ggplot(ggplot2::aes(x=Col96, y=Row96, fill=result)) + 
  ggplot2::geom_raster() +
  ggplot2::coord_equal() +
  ggplot2::facet_grid(~Plate_384+Plate_ID+quadrant_96) +
  #scale_fill_viridis_c(option = 'plasma')+
  ggplot2::ggtitle(params$experiment)
})
```

## Leave Out Tubes QC (96)
```{r echo=FALSE, fig.height=10, fig.width=12}
psplit=split(params$dwide, params$dwide$Plate_384)
lapply(psplit, function(x) {
           x%>%
ggplot2::ggplot(ggplot2::aes(x=Col96, y=Row96, fill=id_tubes)) + 
  ggplot2::geom_raster() +
  ggplot2::coord_equal() +
  ggplot2::facet_grid(~Plate_384+Plate_ID+quadrant_96) +
  #scale_fill_viridis_c(option = 'plasma')+
  ggplot2::ggtitle(params$experiment)
})
```

# Results
```{r echo=FALSE}

dsummary.reduced= params$dwide%>% 
    dplyr::filter(params$samples_with_ids) %>%  
    dplyr::select(Barcode,id_tubes, Plate_96_BC,Pos96, quadrant_96, Plate_384,S2,S2_spike, RPP30,result)

dsummary.reduced %>% 
    tibble::add_column(S2_ratio= round((dsummary.reduced$S2+1)/(dsummary.reduced$S2_spike+1),digits=3),
               .before='result') %>%
    DT::datatable(options=list(pageLength=25,order=list(list(11,'desc'))))%>% 
    DT::formatStyle('id_tubes', target='row', backgroundColor=DT::styleEqual(c(TRUE), c("lightblue"))) %>%
    DT::formatStyle('result', target='row', backgroundColor=DT::styleEqual(c("Positive"), c("pink")))
```



